Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity

### 2025-10-31 preamble.tex
add aggregated file paper_short_in_one.tex
revise the final paper
update recent review opinion and make corr. changes.

@@

>>>>

% --- unify spacing between floats and text (single-/double-column) ---
\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}   % text <-> single-column floats (table/figure)
\setlength{\intextsep}{6pt plus 2pt minus 2pt}      % inline [h] floats
\setlength{\floatsep}{6pt plus 2pt minus 2pt}       % float <-> float (single-column)

\setlength{\dbltextfloatsep}{6pt plus 2pt minus 2pt} % text <-> double-column floats (figure*)
\setlength{\dblfloatsep}{6pt plus 2pt minus 2pt}     % float <-> float (double-column)

% --- caption spacing for tables only ---
\captionsetup[table]{aboveskip=6pt, belowskip=0pt}

@@

\newcommand\wordcount{\input{|"texcount -inc -sum -0 -utf8 -ch -template={SUM} \currfilepath"}}
